$K$-corrections and filter transformations \\ in the ultraviolet, optical, and near infrared

### 2006-06-26 docs/paper/kcorrect.tex
typo
git-svn-id: svn+ssh://howdy.physics.nyu.edu/usr/local/svn/kcorrect/trunk@557 75dff457-8751-0410-ab1a-cd701654ce6b

In this paper, we present a method for doing so, by calculating
$K$-corrections between observed and desired bandpasses.  The
$K$-correction between a bandpass $R$ used to observe a galaxy at
redshift $z$ and the desired bandpass $Q$ is defined by the equation
(\citealt{oke68a, hogg02a}):
\begin{equation}
m_R = M_Q + \mathrm{DM}(z) + K_{QR}(z) - 5 \log_{10} h 
\end{equation}
where $\mathrm{DM}(z) = 25 - 5\log_{10} (d_L / (h^{-1}{\mathrm{~Mpc}}))$ is the
bolometric distance modulus calculated from the luminosity distance
$d_L$, and $M_Q$ is the absolute magnitude. The absolute magnitude is
defined as the apparent magnitude an object would have if were
observed 10 pc away, in bandpass $Q$, at rest.  The traditional
definition of the $K$-correction takes $Q=R$. However, we note that in
practice many surveys do perform $K$-corrections from one observed
bandpass $R$ to another bandpass $Q$ in the rest frame. This practice
is particularly common when dealing with high redshift observations.
In addition to $K$-corrections, this method also provides an
interpretation of the data in terms of a physical model which
describes the stellar mass and star-formation history of each galaxy.

@@

The $K$-correction between a bandpass $R$ used to observe a galaxy at
redshift $z$ and the desired bandpass $Q$ is defined by the equation
(\citealt{oke68a, hogg02a}):
\begin{equation}
\label{kcorrecteqn}
m_R = M_Q + \mathrm{DM}(z) + K_{QR}(z) - 5 \log_{10} h 
\end{equation}
where $\mathrm{DM}(z) = 25 - 5\log_{10} (d_L /
(h^{-1}{\mathrm{~Mpc}}))$ is the bolometric distance modulus
calculated from the luminosity distance $d_L$, and $M_Q$ is the
absolute magnitude. The absolute magnitude is defined as the apparent
magnitude an object would have if were observed 10 pc away, in
bandpass $Q$, at rest.  The traditional definition of the
$K$-correction takes $Q=R$. However, we note that in practice many
surveys do perform $K$-corrections from one observed bandpass $R$ to
another bandpass $Q$ in the rest frame. This practice is particularly
common when dealing with high redshift observations.  In addition to
$K$-corrections, this method also provides an interpretation of the
data in terms of a physical model which describes the stellar mass and
star-formation history of each galaxy.

>>>>

In this paper, we present a method for doing so, by calculating
$K$-corrections between observed and desired bandpasses.  The
$K$-correction between a bandpass $R$ used to observe a galaxy at
redshift $z$ and the desired bandpass $Q$ is defined by the equation
(\citealt{oke68a, hogg02a}):
\begin{equation}
m_R = M_Q + \mathrm{DM}(z) + K_{QR}(z) - 5 \log_{10} h 
\end{equation}
where $\mathrm{DM}(z) = 25 + 5\log_{10} (d_L / (h^{-1}{\mathrm{~Mpc}}))$ is the
bolometric distance modulus calculated from the luminosity distance
$d_L$, and $M_Q$ is the absolute magnitude. The absolute magnitude is
defined as the apparent magnitude an object would have if were
observed 10 pc away, in bandpass $Q$, at rest.  The traditional
definition of the $K$-correction takes $Q=R$. However, we note that in
practice many surveys do perform $K$-corrections from one observed
bandpass $R$ to another bandpass $Q$ in the rest frame. This practice
is particularly common when dealing with high redshift observations.
In addition to $K$-corrections, this method also provides an
interpretation of the data in terms of a physical model which
describes the stellar mass and star-formation history of each galaxy.

@@

The $K$-correction between a bandpass $R$ used to observe a galaxy at
redshift $z$ and the desired bandpass $Q$ is defined by the equation
(\citealt{oke68a, hogg02a}):
\begin{equation}
\label{kcorrecteqn}
m_R = M_Q + \mathrm{DM}(z) + K_{QR}(z) - 5 \log_{10} h 
\end{equation}
where $\mathrm{DM}(z) = 25 + 5\log_{10} (d_L /
(h^{-1}{\mathrm{~Mpc}}))$ is the bolometric distance modulus
calculated from the luminosity distance $d_L$, and $M_Q$ is the
absolute magnitude. The absolute magnitude is defined as the apparent
magnitude an object would have if were observed 10 pc away, in
bandpass $Q$, at rest.  The traditional definition of the
$K$-correction takes $Q=R$. However, we note that in practice many
surveys do perform $K$-corrections from one observed bandpass $R$ to
another bandpass $Q$ in the rest frame. This practice is particularly
common when dealing with high redshift observations.  In addition to
$K$-corrections, this method also provides an interpretation of the
data in terms of a physical model which describes the stellar mass and
star-formation history of each galaxy.
